Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-09-05 paper2.tex
feedback from IF

\begin{abstract}
We report modelling follow-up of recently-discovered
gravitational-lens candidates in the Canada France Hawaii Telescope
Legacy Survey. Lens modelling was done by a small group of
specially-interested volunteers from the \SW citizen-science community
who originally found the candidate lenses.  Models are categorised
according to seven diagnostics indicating (a)~the image morphology and
how clear or indistinct it is, (b)~whether the mass map and synthetic
lensed image appear to be plausible, and (c)~how the lens-model mass
compares with compares with the abundance-matched halo mass derived
from photometry of the lensing galaxy.
The lens-model masses range from $\sim10^{11}M_\odot$ to
$>10^{13}M_\odot$.  Preliminary estimates of the stellar masses show
(with two outliers) a smaller spread in stellar mass: a factor of a
few below or above $\sim10^{11}M_\odot$.  That is, the stellar-mass
fraction declines sharply as lensing mass increases.  The highest-mass
system with a convincing model is J1434+522 (\sw{05}).  The two low-mass
outliers are J0206-095 (\sw{19}) and J2217+015 (\sw{42}); if these two are
indeed lenses, they are probing an interesting regime of very low
star-formation efficiency.
Some improvements to the modelling software used (SpaghettiLens), and
discussion of strategies for scaling to future surveys with more and
frequent discoveries, are also included.
\end{abstract}

\begin{keywords}
gravitational lensing: strong -- galaxies: general
\end{keywords}

>>>>

\begin{abstract}
We report modelling follow-up of recently-discovered
gravitational-lens candidates in the Canada France Hawaii Telescope
Legacy Survey. Lens modelling was done by a small group of
specially-interested volunteers from the \SW citizen-science community
who originally found the candidate lenses.  Models are categorised
according to seven diagnostics indicating (a)~the image morphology and
how clear or indistinct it is, (b)~whether the mass map and synthetic
lensed image appear to be plausible, and (c)~how the lens-model mass
compares with the stellar mass and the abundance-matched halo mass.
The lensing masses range from $\sim10^{11}M_\odot$ to
$>10^{13}M_\odot$. Preliminary estimates of the stellar masses show a
smaller spread in stellar mass (except for two lenses): a factor of a
few below or above $\sim10^{11}M_\odot$.  Therefore, we expect the
stellar-to-total mass fraction to decline sharply as lensing mass
increases.  The most massive system with a convincing model is
J1434+522 (\sw{05}).  The two low-mass outliers are J0206-095
(\sw{19}) and J2217+015 (\sw{42}); if these two are indeed lenses,
they probe an interesting regime of very low star-formation
efficiency.  Some improvements to the modelling software
(SpaghettiLens), and discussion of strategies regarding scaling to
future surveys with more and frequent discoveries, are included.
\end{abstract}

\begin{keywords}
gravitational lensing: strong -- galaxies: general
-- galaxies: stellar content -- dark matter.
\end{keywords}

### 2017-09-05 parts/intro.tex
feedback from IF

\section{Introduction}

By a curious coincidence, the typical escape velocity of massive galaxies is
such that $v_{\rm esc}^2/c^2$ is comparable to the apparent sizes of a
galaxies at cosmological distances.  This coincidence is fortunate,
because it makes the lensing deflection angle (which is $2v_{\rm
  esc}^2/c^2$) of distant galaxies comparable to their size on the
sky, and as a result, strong lensing by galaxies tends to produce
images that probe the dark halos of those galaxies.  This is
important, because while there is a general consensus that basic
mechanism of galaxy formation involves gravitational collapse,
fragmentation, and mergers of dark-matter clumps, into which gas fell,
cooling through radiative processes to form dense clouds and
eventually stars, there is much debate about the details \citep[for a
  summary, see][]{2012RAA....12..917S}.  In particular, the nature of
dark matter remains mysterious: most researchers take it to be a
collisionless non-relativistic fluid (cold dark matter or CDM) readily
studied by simulations \citep[for example, the influential millenium
  simulation by][]{2005Natur.435..629S}.  But other scenarios, where
dark matter has exotic dynamical properties
\citep{2010MNRAS.405...77S,2016ApJ...818...89S}, or is not really
matter at all but a modification of gravity
\citep{2016PhRvL.117t1101M}, have also been considered.

All this motivates using galaxy lenses to study the mutual dynamics of
dark matter, gas and stars in galaxies.  Several studies in recent
years have done so
\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
enlarge the samples from tens of lensing galaxies to thousands.  Doing
so requires both finding more lenses and also modelling their masses.
Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep[e.g.,][]{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G,2017arXiv170401585S}
by machine learning
\citep[e.g.,][]{2016A&A...592A..75P,2017arXiv170302642L} and by visual
inspection by citizen-science volunteers in Space~Warps
\citep{2016MNRAS.455.1191M} have, between them, discovered an average
of four lenses per square degree, so one can be optimistic about
finding many thousands of lenses in the next generation of wide-field
surveys, from the LSST in optical and the SKA in radio on the ground,
and Euclid and WFIRST in orbit.

The expected flood of new lens discoveries will need a similarly huge
modelling effort to reconstruct their mass distributions.  To prepare
for the challenge of massive-sample lens modelling,
\cite{2015MNRAS.447.2170K} developed a new modelling strategy,
implemented as the SpaghettiLens system.  The idea is to collaborate
with experienced members of the citizen-science community, who have
already participated in lens discovery through \SW, as well as several
other projects involving astronomical data.  The system was tested on
a sample of simulated lenses, which were part of the training and
testing set in \SW.

This paper continues that study by applying SpaghettiLens to
lens-candidates discovered through Space~Warps.  We present results
from modelling of 58 of the 59 lens candidates reported by
\cite{2016MNRAS.455.1191M}.  Each lens candidate was modelled in a
collaborative refinement process, where anyone interested can create a
new model or modify an existing model to try and make it
better.\footnote{This is in contrast to the main Space~Warps project
  for discovering lenses, where volunteers in a crowd of $\gtrsim10^4$
  make independent contributions.  Each person is presented with a
  random selection of survey-patches and invited to (in effect) vote
  on each.  The system estimates each volunteer's skill level
  according to test-patches interspersed with the real data, and
  weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There
  is an active forum for volunteers, but since everyone is seeing
  different data samples with minimal overlap, the forum has little if
  any influence on votes.}  The resulting model represents a consensus
among contributors, as to the best that could be achieved with the
available data and software.

Interpretation of the results is tentative,
because the systems are lens candidates at this stage, not secure lenses.
Moreover the candidate-lens redshifts have large uncertainties, while
the candidate-source redshifts can only be guessed at present.
Nevertheless it is interesting to see what trends we can observe with
the already-available data.
%TODO there is more info about uncertainies here:
% https://arxiv.org/pdf/0811.3326.pdf

This paper is organized as follows:
Section~\ref{sec:candidates_models} introduces the candidates, the models and the diagnostics applied to them.
The following sections elaborate on the diagnostics.
Image morphology diagnostics are explained in Section~\ref{sec:morph} and
diagnostics based on the mass models in Section~\ref{sec:massmodels}.
Stellar masses are calculated in Section~\ref{sec:stellar-mass} to compare stellar to lensing masses of the candidates.
Section~\ref{sec:summary} summarises and tabulates the diagnostics in
Table~\ref{tab:models}.

There are three appendices devoted to various technical issues
relating to modelling.
The online supplement gives results for all the modelled systems generated
for all the lensing candidates.

\section{The candidates and models}
\label{sec:candidates_models}

\SW is a citizen science gravitational lens search \citep{2016MNRAS.455.1171M}.
Its first run searched the CFHT Legacy Survey, a survey carried out in five optical bands ($u^*$,$g'$,$r'$,$i'$,$z'$) covering a total area of 160 \sqdeg divided up into four fields W1 -- W4.
It has a field of view of 1 \sqdeg, a pixel size of 0.186'' and the deepest limiting magnitude is 25.47 in the $g$ band \citep{2012AJ....143...38G}.
The cutouts shown to the volunteers were colour composites of the $g$, $r$ and $i$ band of randomly chosen regions.
It resulted in 59 new (of which 29 promising) lens candidates that have not been found by other searches already and in the rediscovery of 82 previously known lens candidates.
The candidates have broadly similar redshifts (0.2 -- 1.0), Einstein radii (0.7\arcsec -- 5\arcsec) and arc magnitudes (22 -- 26) as those found by previous robotic searches like ArcFinder and RingFinder \citep{2016MNRAS.455.1191M}.

@@

A first version of \SpL was launched in May 2013, while the first run of \SW was ongoing.
Figure~\ref{fig:time} shows the total number of models generated since launch, but only includes models for the lens candidates.
A small number of volunteers started to work with \SpL to create models of possible lens candidates found in \SW that were debated on in the \SW discussion forums.
In the beginning of August 2013 (around day 70) a modelling challenge for the candidate later to be identified as \sw{01} was launched.
A group of five volunteers converged to a set of favourite models that they presented in an online letter after about 65 days passed and 30 models have been created for this particular system.
In April 2015 (day 700) the first major release of \SpL was presented.
In the same time the list of identified candidates was made available \citep[as a preprint of][]{2016MNRAS.455.1191M}.
At this stage, the volunteers were asked to create models for all the lens candidates that were still missing.
The generated models for candidate \sw{29} show that the volunteers converged to a favourable model much faster, after 15 models generated in 30 days.

This modelling effort resulted in a total set of 377 \SpL models for all but one of the 59 \SW lens candidates; candidate \sw{39} was not modelled by any volunteer.
Over its runtime the system saw eight major contributors (volunteers that at least generated five models each).

In parallel \cite{2015MNRAS.447.2170K} tested the system
on simulated lenses and identified some areas for improvement.  In
\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
profiles of the source.  This feature has not yet been included in
SpaghettiLens, but has been carried out in post-processing for a few
especially interesting candidates.  In \S~\ref{subsec:hires} we show
that making mass maps fine-grained in the central region relieves a
tendency in the earlier work for mass profile to be too shallow. Then in
\S~\ref{subsec:parameter} we consider the possibility of fitting a
parametric lens model to the model ensemble; so far we have only been
successful at extracting an Einstein radius.

We characterise each model with seven diagnostics, grouped into three 
categories, whose purpose is to help identify which systems are most probably 
lenses, and which ones are likely to be most rewarding for future follow-up 
observations. The diagnostics are as follows.

\begin{itemize}
\item First we have diagnostics based on morphology of the
  system.
  Section~\ref{sec:morph} and Figure~\ref{fig:splinput} explain.
\begin{enumerate}
\item Whether the images are unblended.  Distinct unblended images are
  an advantage in modelling, but not essential.
\item Whether all images are discernible.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible, in which case the modeller has to
  insert conjectural image positions.
\item Whether the lens is fairly isolated.
\item The image morphology concisely described: double or quads,
  further sub-categorised to indicate the elongation direction of the
  lensing mass.
\end{enumerate}
\item Second we have mass models, covered in Section~\ref{sec:massmodels}.
\begin{enumerate}
\setcounter{enumi}{4}
\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
\item Whether the arrival-time surface and synthetic image are
  plausible.  In particular, additional images are implied in regions
  where they are not observed signal an unsatisfactory model.
  Figures~\ref{fig:arriv} and \ref{fig:synth} and \ref{fig:encl}.
\end{enumerate}
\item Third, whether the total implied lensing mass
  determined from the lens model is plausible, given the
  photometry of the lensing galaxy.
  In this work we define lensing mass as the sum of all mass tiles
  needed to model a lens. These mass tiles reach out to typically twice
  the radius of the the outermost image.
  Section~\ref{sec:stellar-mass}
  explains how we compare the lensing mass with the mass in stars in
  the lensing galaxy.  We estimate the stellar mass by comparing
  galaxy magnitudes from the CFHTLS pipeline with the well-known
  stellar-population models of \cite{2003MNRAS.344.1000B}.  We then
  extrapolate the stellar mass to a halo mass using the
  abundance-matching prescription of \cite{2010ApJ...710..903M}.
  Naturally, the lensing mass must be more than the stellar mass but
  no more than the total halo mass.
\begin{enumerate}
\setcounter{enumi}{6}
\item We then introduce what we call a halo index ($\haloindex$) which
  gives an idea of how the lensing mass compares with these two
  constraints.  Figure~\ref{fig:stelmass}.
\end{enumerate}
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

By a curious coincidence, the typical escape velocity of massive
galaxies -- of order a few hundred km/s -- is such that $v_{\rm
  esc}^2/c^2$, expressed as an angular distance, is comparable to the
apparent sizes of galaxies at cosmological distances.  This
coincidence is fortunate, because it makes the gravitational lensing
deflection angle of distant galaxies ($\alpha\sim 2v_{\rm esc}^2/c^2$)
comparable to their size on the sky. As a result, strong lensing by
galaxies produces images that probe their host dark matter halos,
providing a useful tool to understand galaxy formation.  While there
is a general consensus about the basic mechanisms at play, involving
gravitational collapse, fragmentation, and mergers of dark-matter
clumps, into which gas fell, cooling through radiative processes to
form dense clouds and eventually stars, there is much debate about the
details \citep[for a summary, see][]{2012RAA....12..917S}.  In
particular, the nature of dark matter remains mysterious: most
researchers take it to be a collisionless non-relativistic fluid (cold
dark matter or CDM) readily studied by simulations \citep[for example,
  the influential Millennium
  simulation,][]{2005Natur.435..629S}. However, alternative scenarios,
where dark matter has exotic dynamical properties
\citep{2010MNRAS.405...77S,2016ApJ...818...89S}, or is not really
matter at all, but a modification of gravity
\citep{2016PhRvL.117t1101M}, have also been considered.

All this motivates the use of strong gravitational lensing over galaxy
scales to study the mutual dynamics of dark matter, gas and stars.
Several studies in recent years have done so \citep[see,
  e.g.,][]{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
enlarge the samples from tens of lensing galaxies to thousands.  Doing
so requires both finding more lenses and also modelling their mass
distribution.  Recent searches through the CFHT Lens Survey
\citep[CFHTLS,][]{2012MNRAS.427..146H} using arc-finders
\citep[e.g.,][]{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G,2017arXiv170401585S}
by either machine learning methods 
\citep[e.g.,][]{2016A&A...592A..75P,2017arXiv170302642L} or visual
inspection by citizen-science volunteers through the \SW project 
\citep{2016MNRAS.455.1191M} have, between them, discovered an average
of four lenses per square degree, so one can be optimistic about
finding many thousands of lenses in the next generation of wide-field
surveys, from ground-based surveys such as LSST in the optical window
and SKA in radio, to space-based missions such as Euclid and WFIRST.

The expected flood of new lens discoveries will need a equally large
modelling effort to reconstruct their mass distributions.  To prepare
for the challenge of massive-sample lens modelling,
\cite{2015MNRAS.447.2170K} developed a new modelling strategy,
implemented as the SpaghettiLens system.  The idea is to collaborate
with experienced members of the citizen-science community, who have
already participated in the discovery of gravitational lenses through
\SW, as well as in several other projects involving astronomical data.
The system was tested on a sample of simulated lenses, that were part
of the training and testing set in \SW.

This paper follows up that study by applying SpaghettiLens to
candidates discovered through \SW.  We present results from
the modelling of 58 of the 59 lens candidates reported by
\cite{2016MNRAS.455.1191M}.  Each lens candidate was modelled
following a collaborative refinement process, where anyone interested
could improve the analysis by modifying an existing model or creating
a new one. Note the difference with respect to the main \SW 
project, where volunteers from a group of $\gtrsim10^4$ people make
independent contributions.  Each person is presented with a random
selection of survey-patches and invited to (in effect) vote on each.
The system estimates the skill level of each volunteer according to
test-patches interspersed with the real data, and weights their votes
accordingly \citep{2016MNRAS.455.1171M}.  There is an active forum for
volunteers, but since everyone is seeing different data samples with
minimal overlap, the forum has little if any influence on the votes.
\textcolor{red}{\bf IF: Please make sure the following is correct:}
In SpaghettiLens, the number of volunteers is significantly lower, but
the level of interaction is higher.  The resulting model represents a
consensus among contributors, as to the best that could be achieved
with the available data and software.

We emphasize that the interpretation of the results presnted here is
tentative, because the systems are lens candidates at this stage, not
secure lenses.  Moreover the candidate-lens redshifts have large
uncertainties, while the candidate-source redshifts can only be
guessed at present.  Nevertheless it is interesting to explore the
trends observed with the already available data.
%TODO there is more info about uncertainies here:
% https://arxiv.org/pdf/0811.3326.pdf

This paper is organized as follows:
Section~\ref{sec:candidates_models} introduces the candidate lenses,
their models and the diagnostics applied to them.  The following
sections elaborate on the diagnostics.  Image morphology diagnostics
are explained in Section~\ref{sec:morph} and diagnostics based on the
mass models are discussed in Section~\ref{sec:massmodels}.  Stellar masses are
presented in Section~\ref{sec:stellar-mass}, to compare stellar and
lensing masses.  Finally, section~\ref{sec:summary}
summarises and tabulates the diagnostics in Table~\ref{tab:models}.

We include three appendices devoted to various technical issues
relating to the modelling.  The online supplement gives the results
from all the modelled systems generated for all the lensing
candidates.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The candidates and models}
\label{sec:candidates_models}

\SW is a citizen science gravitational lens search
\citep{2016MNRAS.455.1171M}.  Its first run searched the CFHT Legacy
Survey, a survey carried out in five optical bands
($u^*$,$g^\prime$,$r^\prime$,$i^\prime$,$z^\prime$) covering a total
area of 160\,\sqdeg divided up into four fields W1 -- W4.  The
MegaPrime camera, used for the survey, has a field of view of
1\,\sqdeg, with 0.186$^{\prime\prime}$ pixels. The flux limit of the
survey is $g^\prime<$25.6AB (5\,$\sigma$) with a typical seeing
FWHM$\sim 0.7^{\prime\prime}$ \citep{2013MNRAS.433.2545E}. The cutouts
shown to the volunteers were colour composites of the $g^\prime$,
$r^\prime$ and $i^\prime$ bands from randomly chosen regions.
The programme \citep{2016MNRAS.455.1191M} resulted in 59 new lens candidates (of which 29 are
promising  \textcolor{red}{\bf IF: why are
  they promising? explain this here).}  Moreover, 82 previously known
lens candidates were ``rediscovered''.  The candidates have broadly
similar redshifts (0.2$<$z$<$1.0), Einstein radii between 0.7 and
5\,\arcsec, and arc magnitudes between 22 and 26 \textcolor{red}{\bf
  IF: in the $g^\prime$ band?}. These properties are similar to those
found by previous robotic searches like ArcFinder and RingFinder.

@@

A first version of \SpL\footnote{\textcolor{red}{\bf IF include web
    link: {\tt http://xxx.yyy.ch}}} was launched in May 2013, while
the first run of \SW was ongoing.  Fig.~\ref{fig:time} shows the
total number of models generated since launch for our lens candidates.
A small number of volunteers started creating models of possible lens
candidates from \SW that were debated in the discussion forum.  In the
beginning of August 2013 (around day 70 since release) a modelling
challenge for the candidate later to be identified as \sw{01} was
launched.  A group of five volunteers presented their results in an
online letter \textcolor{red}{\bf REFERENCE?} about 65 days later,
converging on a set of 30 models. In April 2015 (day 700),
the first major version of \SpL was released. At the same time,
the list of identified candidates was made available \citep[as a preprint
  of][]{2016MNRAS.455.1191M}.  At this stage, the volunteers were
asked to create models for all the lens candidates that were still
missing.  The work done for candidate \sw{29} show that the
volunteers converged on a favourable model much faster, after 15
models, generated in 30 days.  The total modelling effort resulted in
a set of 377 \SpL models for all but one of the 59 \SW lens
candidates; candidate \sw{39} was not modelled by any volunteer.  Over
its runtime, the system logged eight major contributors (defined as
volunteers that generated, at least, five models).

In parallel, \citet{2015MNRAS.447.2170K} tested the system on
simulated lenses and identified some areas for improvement.  In
\S~\ref{subsec:sourcefit} we introduce fitting of the surface
brightness profile of the source.  This feature has not been included
yet in SpaghettiLens, but we carried the analysis during
post-processing for a few interesting cases.  In \S~\ref{subsec:hires}
we show that fine-grained mass maps within the central region
relieves a tendency in the earlier work for mass profiles to be too
shallow. In \S~\ref{subsec:parameter} we consider the possibility
of fitting a parametric lens model to the ensemble.
%; so far we have only been successful at extracting an Einstein radius.

We characterise each model with seven diagnostics, grouped into three
categories, whose purpose is to help identify the most likely cases of
a gravitational lens, as well as flag the most interesting candidates
for future follow-up observations. The diagnostics are as follows.

\begin{itemize}
\item Firstly we have diagnostics based on morphology.
  Section~\ref{sec:morph} and Fig.~\ref{fig:splinput} explain
  this diagnostic in more detail. We consider:
\begin{enumerate}
\item Whether the images are unblended:  Distinct, unblended images are
  an advantage in modelling, although not essential.
\item Whether all images are discernible.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible, in which case the modeller has to
  insert conjectural image positions.
\item Whether the lens is isolated.
\item The image morphology concisely described: double or quads,
  further sub-categorised to indicate the elongation direction of the
  lensing mass.
\end{enumerate}
\item Secondly we have mass models, covered in Section~\ref{sec:massmodels}.
  We assess the following points:
\begin{enumerate}
\setcounter{enumi}{4}
\item Whether the mass map is reasonable (see Fig.~\ref{fig:kappa}).
\item Whether the arrival-time surface and synthetic image are
  plausible. In particular, an unsatisfactory model is flagged when 
  additional images are implied in regions
  where they are not observed (see Figs.~\ref{fig:arriv}, \ref{fig:synth} \ref{fig:encl}).
\end{enumerate}
\item Thirdly, whether the total implied lensing mass determined from
  the lens model is plausible, given the photometry of the lensing
  galaxy.  In this work we define the lensing mass as the sum of all
  mass tiles in the model.  These mass tiles reach out to typically
  twice the radius of the outermost image.
  Section~\ref{sec:stellar-mass} explains how we compare the lensing
  (i.e. total) mass with the stellar mass. Naturally, the lensing
  mass should be somewhere between the stellar mass (lower bound)
  and the total halo mass (upper bound).
\begin{enumerate}
\setcounter{enumi}{6}
\item We then introduce a so-called halo index ($\haloindex$), that
  quantifies how the lensing mass compares with these two
  constraints (see Fig.~\ref{fig:stelmass}).
\end{enumerate}
\end{itemize}

### 2017-09-05 parts/massmodel.tex
z errors
feedback from IF

\section{Mass models}\label{sec:massmodels}

Once a spaghetti diagram has been drawn on a web browser, it is
forwarded to a server-side numerical framework, which searches for
mass maps consistent with the given image locations, parities and time
ordering.  The mass maps are made up of mass tiles and are free-form,
but are required to be concentrated around the identified lens centre
\citep[see][for the precise formulation of the search
  problem.]{2014MNRAS.445.2181C} Assuming such mass distributions can
be found (which in practice is usually the case) a statistical
ensemble of two-dimensional mass maps is returned.  This ensemble,
along with derived quantities and uncertainties, makes up one
SpaghettiLens model.

The mass will naturally depend on the lens and source redshifts, which
are unknown when a lens candidate is first identified.  But this is
not a problem, because a model can be trivially rescaled to use better
redshift values, as and when they become available.  This work applies
photometric redshifts from the CFHTLS pipeline to the candidate
lensing galaxies; the values range from $z=0.2$ to $z=1$ (see
Table~\ref{tab:models}).  As the mass normalisation depends only weakly
on source redshift, provided it is larger than the lens redshift,
we assumed all sources to lie at $z=2$ unless an unambiguous photometric
redshift is available.

@@

Figure~\ref{fig:arriv} shows arrival-time surfaces corresponding to
the spaghetti diagrams in Figure~\ref{fig:splinput}.  The arrival-time
contours look like machine-made elaborations of the input spaghetti
diagrams.  If the saddle-point contours in the arrival time are
qualitatively the same as the curves in the spaghetti diagram (the
detailed shape of the spaghetti curves is unimportant), it immediately
suggests a successful model.  On the other hand, if the arrival-time
surface has unexpected minima or saddle points, and especially if the
unexpected features are far from identified lens images, that signals
a doubtful model.  Figure~\ref{fig:synth} shows what we call synthetic
images, meaning reconstructions of the extended lensed features by
fitting for a source.  These were generated by a new method, explained
in Appendix~\ref{subsec:sourcefit}, implemented in offline
post-processing after the modelling process was complete.  The
synthetic images provided by SpaghettiLens during the collaborative
modelling and discussion were more crude; these are included in the
online supplement.

The arrival-time surface and synthetic image are summarised by one
diagnostic, the most important of all: are the lensed features
satisfactorily reproduced?  This diagnostic remains a judgment call by
modellers.  A useful quantitative criterion for whether the synthetic
image is consistent with the data would need to allow for PSF
dependence and unmodelled substructure ---otherwise all models would
be summarily rejected--- and it is not clear how to do this.

Figure~\ref{fig:kappa} shows projected mass maps of the example
systems.  Actually, this figure only shows the ensemble-average mass
maps, and not the variation within the ensemble, from which
uncertainties can be inferred.  (The same applies to the arrival-time
surfaces and synthetic images in the two previous figures.
Uncertainties will be shown in a concise form later, with
Figure~\ref{fig:encl}.)  Figure~\ref{fig:kappa} makes evident the
tiled nature of the mass model.  The tiles can be smoothed over by
interpolating, and this was actually done in the mass maps shown
online during the modelling process.  It is interesting, however, to
see the tiling artifacts, if only as a reminder that the substructure
in the mass distribution are very uncertain, even if some integrated
quantities are very well constrained.  How the free-form mass maps
relate to parameterised lens models is discussed in
Appendix~\ref{subsec:parameter}.  Note that the arrival-time surface
does not have discontinuous jumps, because the modelling numerics uses
an analytical integral over square tiles; likewise the lens equation.

Figure~\ref{fig:encl} shows the enclosed-mass profiles,
expressed as the average convergence $\kappa$ within circles of given
projected radius.  This time, uncertainties are included.
Appendix~\ref{subsec:hires} describes improvements made since our
earlier work \citep{2015MNRAS.447.2170K}, to allow for steeper
profiles in the inner regions.  The enclosed mass is typically best
constrained at the notional Einstein radius, becoming more uncertain
at larger and smaller radii.

The mass maps and mass profiles are the basis of a further diagnostic:
are the mass distributions plausible?

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Mass models}\label{sec:massmodels}

Once a spaghetti diagram has been drawn on a web browser, it is
forwarded to a server-side numerical framework, which searches for
mass maps consistent with the image locations, parities and time
ordering, given by the modeller.  The mass maps are made up of mass
tiles and are free-form, but are required to be concentrated around
the identified lens centre \citep[see][for the precise formulation of
  the search problem]{2014MNRAS.445.2181C}. Assuming such mass
distributions can be found -- which in practice is usually the case --
a statistical ensemble of two-dimensional mass maps is returned.  This
ensemble, along with derived quantities and uncertainties, makes up
one SpaghettiLens model.

The mass will naturally depend on the lens and source redshifts, which
are unknown when a lens candidate is first identified.  However, this
is not a problem, because a model can be trivially rescaled to use
better redshift values, as they become available.  This work applies
photometric redshifts from the CFHTLS pipeline
\citep{2009A&A...500..981C} to the candidate lensing galaxies; the
values range from z=0.2 to 1 (see Table~\ref{tab:models}).
These redshifts entail rather big uncertainties, up to a few ten
percent.  Since, however, the angular critical density is proportional
to $d_l d_s d_{ls}^{-1}$ \citep[consult Equation~A1
  in][]{2015MNRAS.447.2170K} it is negligible for this tentative
analysis. \textcolor{red}{\bf IF: I would not say this is
  ``negligible'' but, rather, that the error in the redshift would lead to
  surface mass density uncertainties of XX\%, which, for the
  aim of the tentative analysis presented here, is an acceptable
  result. You should also check and quantify properly the
  uncertainty in the photo-z. What is the value claimed by the
  CFHTLS group? I would say 5-10\% is a decent level, but you
are mentioning 10s of \% which is rather extreme!}.
As the mass normalisation depends only weakly on the source redshift,
provided it is higher than the lens redshift, we adopted a redshift
z=2 for all sources, unless an unambiguous photometric redshift is
available. \textcolor{red}{\bf IF: Again, a simple quantification of the
change you expect, for instance, if the source is at z=3 would be good.}

@@

Fig.~\ref{fig:arriv} shows the arrival-time surfaces corresponding to
the spaghetti diagrams of Fig.~\ref{fig:splinput}.  The arrival-time
contours look like machine-made elaborations of the input spaghetti
diagrams.  If the saddle-point contours in the arrival time are
qualitatively the same as the curves in the spaghetti diagram (the
detailed shape of the spaghetti curves is unimportant), it immediately
suggests a successful model.  On the other hand, if the arrival-time
surface has unexpected minima or saddle points, and especially if the
unexpected features are far from identified lens images, that signals
an improbable model.  Fig.~\ref{fig:synth} shows what we call synthetic
images, meaning reconstructions of the extended lensed features by
fitting for a source.  These were generated by a new method, explained
in Appendix~\ref{subsec:sourcefit}, implemented during the offline
post-processing after the modelling process was complete.  The
synthetic images provided by SpaghettiLens during the collaborative
modelling and discussion were more crude; those are included in the
online supplement.

The arrival-time surface and synthetic image are summarised by one
diagnostic, the most important of all: are the lensed features
satisfactorily reproduced?  This diagnostic remains a judgment call by
modellers.  A useful quantitative criterion for whether the synthetic
image is consistent with the data would need to allow for PSF
dependence and unmodelled substructure -- otherwise all models would
be summarily rejected, something left for a future implementation
in SpaghettiLens.

Fig.~\ref{fig:kappa} shows the projected mass maps of the sample.  In
fact, this figure only shows the ensemble-average mass maps, and not
the variation within the ensemble, from which uncertainties can be
inferred. The same applies to the arrival-time surfaces and synthetic
images in the previous two figures. The uncertainties will be shown in
a concise form in Fig.~\ref{fig:encl}.  Fig.~\ref{fig:kappa} makes
evident the tiled nature of the mass model.  The tiles can be smoothed
over by interpolation, and this was done in the mass maps during the
modelling process, available in the online version.  It is
interesting, however, to note the tiling artifacts, if only as a
reminder that the substructure in the mass distribution is very
uncertain, even if some integrated quantities are  well
constrained.  How the free-form mass maps relate to parameterised lens
models is discussed in Appendix~\ref{subsec:parameter}.
\textcolor{red}{{\bf IF: This sentence is confusing and needs some
    clarification:} Note that the arrival-time surface does not have
  discontinuous jumps, because the modelling numerics uses an
  analytical integral over square tiles; likewise the lens equation.}

Fig.~\ref{fig:encl} shows the enclosed-mass profiles, expressed as the
average convergence, $\kappa$, within circles of given projected
radius.  The uncertainties \textcolor{red}{\bf IF: at the BLAH level}
are included.  Appendix~\ref{subsec:hires} describes the improvements made
since our earlier work \citep{2015MNRAS.447.2170K}, to allow for
steeper profiles in the inner regions.  The enclosed mass is typically
best constrained at the notional Einstein radius, becoming more
uncertain at larger and smaller radii.

The mass maps and mass profiles are the basis of a further diagnostic:
are the mass distributions plausible? This is also a judgment call
made by modellers, but it showed to be a powerful diagnostic,
summarizing three aspects. The overall shape is forced to be
$180^\circ$-rotation symmetric, usually a plausible assumption, but
volunteers can deactivate this constraint. The profile slope turned
out to be a good indicator of plausible models, as can seen by
contrasting model \sw{57} with the rest of the sample:  The missing
core in Fig.~\ref{fig:kappa} and the flat profile in
Fig.~\ref{fig:encl} disqualify this model. The clumpiness of the
mass map is another useful indicator. Flat profile slopes can often be
identified directly in the mass map, where the mass tiles form a
checkerboard pattern.
